Modular Model-Checking Implementations of a Byzantine Fault-Tolerant Protocol

### 2016-12-08 doc/om-paper/paper.tex
more wibbles.

\begin{figure}
  \centering
  \begin{tabular}{|p{3cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
  \hline
                                  & Transition systems\linebreak (7 total)  &Definitions\linebreak (58 total) & Invariants\linebreak (11 total) & Invariant classes\linebreak (5 total) \\
  \hline \hline
  No Fault Model                  & receivers & 8 modified & 2 modified & ASM, faults \\
  \hline
  Omissive Asymmetric Faults       & none      & 4 modified & 2 modified & faults             \\
  \hline
  Time-Triggered Messaging        & source, relays, receivers, ASM & 3 new & 2 modified, 3 modified & calendar, faults \\
  \hline
  Mid-Value Selection & receivers & 4 new, 3 modified & 2 modified & ASM, voting \\
  \hline
  \end{tabular}
  \caption{Refactoring effort for protocol modifications, measured by which portions of the model have to be modified.}
  \label{fig:effort}
\end{figure}

@@

\lee{no paragraph on no faults in table?}

@@

Adding new kinds of faults requires more work but is still modular. Consider adding \emph{omissive asymmetric faults}, a restriction of Byzantine faults in which a broadcaster either sends the correct value or a benign fault~\cite{omissive}, to the fault model. Doing so requires modifying none of transition systems. However, we modify four definitions (\texttt{msg()}, characterizing the result on the calendar due to a faulty message; \texttt{omissive\_asymmetric\_fault\_constraint()}, defining the fault, and two functions that characterize the overall maximum fault assumption). Two invariants, both in the class of invariants cover faults, are extended to cover the cases where a sender is omissive asymmetric.

@@

The Oral Messages algorithm and its variants and its variants have a long history of formal verification. \OM{1} was verified in both the PVS and ACL2 interactive theorem-provers~\cite{Young97:IC}. Also in ACL2, an implementation of a circuit design to implement \OM{1} is given~\cite{om-acl2-impl}; the low-level model most closely relates to our level of detail. A refinement-based verification approach is used, and \OM{1} is specialized to a four-node system. It appears that a general purpose voting algorithm (like Fast MJRTY) is not verified as part of the work. A hybrid fault-model and modified Oral Messages algorithm was developed by Thambidurai and Park~\cite{hybrid}. Using the PVS interactive theorem-prover~\cite{pvs}, Lincoln and Rushby demonstrate a flaw in Thambidurai and Park's algorithm and present a fix to it~\cite{Lincoln-Rushby}.

@@

Beyond building an ADSL, another avenue of research is producing a formal proof that a software implementation satisfies the node specification in our framework. While our model of node behavior is low-level, there are gaps. For example, our work is in SAL's language of guarded commands~\cite{SAL} and needs to be either refined or verified to be equivalent to a software implementation's semantics. Another aspect is that behavior related to networking and benign fault diagnosis (e.g., computing a CRC) is are left abstract. In a software implementation, the \texttt{send()} and \texttt{recv()} functions would have to implement these behaviors. Finally, we have modeled messages as integers; but real data may be more complex. A synthesis approach may be suitable and has been used in the past for fault-tolerant clock-synchronization~\cite{ddd}.

>>>>

\begin{figure}
  \centering
  \begin{tabular}{|p{3cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
  \hline
                                  & Transition systems\linebreak (7 total)  &Definitions\linebreak (58 total) & Invariants\linebreak (11 total) & Invariant classes\linebreak (5 total) \\
  \hline \hline
  %% No Fault Model                  & receivers & 8 modified & 2 modified & ASM, faults \\
  %% \hline
  Omissive Asymmetric Faults       & none      & 1 new, 2 modified & 2 modified & faults             \\
  \hline
  Time-Triggered Messaging        & source, relays, receivers, ASM & 3 new & 2 modified, 3 modified & calendar, faults \\
  \hline
  Mid-Value Selection & receivers & 4 new, 3 modified & 2 modified & ASM, voting \\
  \hline
  \end{tabular}
  \caption{Refactoring effort for protocol modifications, measured by which portions of the model have to be modified.}
  \label{fig:effort}
\end{figure}

@@

@@

Adding new kinds of faults requires more work but is still modular. Consider adding \emph{omissive asymmetric faults}, a restriction of Byzantine faults in which a broadcaster either sends the correct value or a benign fault~\cite{omissive}, to the fault model. Doing so requires modifying none of transition systems. We add a new uninterpreted function definition for omissive asymmetric faults, then modify the type of faults, and their effect on the calendar. Two invariants, both in the class of invariants cover faults, are extended to cover the cases where a sender is omissive asymmetric.

@@

The Oral Messages algorithm and its variants and its variants have a long history of formal verification. \OM{1} was verified in both the PVS and ACL2 interactive theorem-provers~\cite{Young97:IC}. Also in ACL2, an implementation of a circuit design to implement \OM{1} is given~\cite{om-acl2-impl}; the low-level model most closely relates to our level of detail. A refinement-based verification approach is used, and \OM{1} is specialized to a four-node system. It appears that a general purpose voting algorithm (like Fast MJRTY) is not verified as part of the work. It is not clear how difficult it would be to model and verify changes to the implementation in that framework.

@@

Beyond building an ADSL, another avenue of research is producing a formal proof that a software implementation satisfies the node specification in our framework. While our model of node behavior is low-level, there are gaps. For example, our work is in SAL's language of guarded commands~\cite{SAL} and needs to be either refined or verified to be equivalent to a software implementation's semantics. Another aspect is that behavior related to networking and benign fault diagnosis (e.g., computing a CRC) is are left abstract. In a software implementation, the $send$ and $recv$ functions would have to implement these behaviors.

 %% A synthesis approach may be suitable and has been used in the past for fault-tolerant clock-synchronization~\cite{ddd}.
